---
title: "Music Insights"
author: "Olivia Lund"
output: html_notebook
---

First, we need tidyverse to handle data importing and wrangling...

```{r}
#install.packages("tidyverse")

survey <- read.csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/music-survey.csv")
preferences <- read.csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/preferences-survey.csv")

```

The data in the music survey table has inconsistent and verbose naming that isn't conducive to good datakeeping. We can change the column names to better represent 
Cleaning data frame column names:
```{r}
colnames(survey)[colnames(survey)=="Timestamp"]<-"time_submitted"
colnames(survey)[colnames(survey)=="First..we.are.going.to.create.a.pseudonym.for.you.to.keep.this.survey.anonymous..more.or.less...Which.pseudonym.generator.would.you.prefer."]<-"pseudonym_generator"
colnames(survey)[colnames(survey)=="What.is.your.pseudonym."]<-"pseudonym"
colnames(survey)[colnames(survey)=="Sex"]<-"sex"
colnames(survey)[colnames(survey)=="Major"]<-"academic_major"
colnames(survey)[colnames(survey)=="Academic.Year"]<-"academic_level"
colnames(survey)[colnames(survey)=="Year.you.were.born..YYYY."]<-"year_born"
colnames(survey)[colnames(survey)=="Which.musical.instruments.talents.do.you.play...Select.all.that.apply."]<-"instrument_list"
colnames(survey)[colnames(survey)=="Artist"]<-"favorite_song_artist"
colnames(survey)[colnames(survey)=="Song"]<-"favorite_song"
colnames(survey)[colnames(survey)=="Link.to.song..on.Youtube.or.Vimeo."]<-"favorite_song_link"

colnames(survey)

#colnames(survey)[colnames(survey)=="timestamp"]<-"time_submitted" #sidenote: this doesn't work. Why?
```

This dataset completely encapsulates the data, but it describes several types of things, and has columns that describe multiple pieces of information, violating the principles of tidy data. In order to resolve this, the table will need to be neatly divided.

```{R}
library(tidyverse)
library("dplyr")
```

First, let's create a person table with each of the responses from the survey. This table should include pseudonym_generator_name, pseudonym, sex, academic_major, academic_level, and year_born:

```{R}
person<-tibble(pseudonym_generator_name = survey$pseudonym_generator_name,  sex = survey$sex, )
```